Designing Qusecs Optimally: Quasi-uniform or Self-similar Layered Materials as Recursively Decomposed Solutions of Geometric Constraint Systems

### 2014-12-15 doc/GMP2015/s01_introduction.tex
Major changes to my section. Meera's major changes to her sections. Updated labels and their references.

\section{Introduction}
\label{sec:prev}

Some properties of natural and engineered materials can be analyzed  by
treating them as stacked two dimensional (2D) layers.
The structure within each layer could be
self-similar \cite{Intro1}
spanning multiple scales,
generally aperiodic and quasi-uniform within any one scale,
and consisting of a few repeated motifs appearing in disordered
arrangements. Each layer is not necessarily planar, i.e.,
it consists of multiple,
inter-constraining planar (genus 0) monolayers.
Furthermore, a layer is often  either
{\sl isostatic or underconstrained, not
self-stressed} (See Section \ref{prelim} for definitions).
These properties are
consistent with a self-assembled 2D structure that minimizes mass,
optimally distributes external stresses and itself
participates in the assembly of diverse and multifunctional,
larger 2D structures.

@@

\begin{enumerate}
  %
    \item (cross-section) of microtubules \cite{Necklace1} e.g., in
ciliary membranes and transitions \cite{Necklace2}
   %
    \item (cross-section) of hierarchical bone structure \cite{XX} %
    \item crosslinked cellulose or collagen microfibril monolayers e.g.,
in cell-walls \cite{CellWalls1} \cite{CellWalls1}, as well as crosslinked
actin filaments in the cytoskeleton matrix.
  %
    \item more recent, engineered examples including  disordered graphene
layers \cite{Graphene1} \cite{Graphene2} sometimes reinforced
    by  microfibrils; and DNA assemblies \cite{Microfibrils1} including a
recent Sierpinski carpet, bringing other self-similar structures
    \cite{Microfibrils2} within reach.
    %
    \item  silica bi-layers, glass \cite{SilicaGlass1}
\cite{SilicaGlass2}, and materials that behave like assemblies of
    2D particles under non-overlap constraints, e.g, jammed
    disks on the plane \cite{JammedDisk1}
%
\end{enumerate}
%
In order to study structural and mechanical properties
such as rigidity, flexes and distribution of external stresses
within the material layer, it is natural to model a material
layer as a solution of a geometric constraint system
of appropriate types of geometric primitives, under
metric or algebraic constraints.
Such  2D {\bf{\em qusecs}} (quasi-uniform or self-similar
constraint systems) can be used to
understand or design material layers (their solutions)
with desired properties.
%
\subsection{Previous Work on Relevant 2D Geometric Constraint Systems} We
now briefly survey existing techniques for studying 2D {\em qusecs,}  many
of which are {\it bar-joint} systems (Examples 1,2 above, see Sections
\ref{dr}, \ref{recomb}),
{\it multibody-pin} systems (Example 4,5, see Section \ref{app}) or  {\it
pinned-line incidence} systems (Example 3, see Section \ref{app}). The
limitations of these techniques directly motivate
the contributions of this paper.

@@

\medskip\noindent\underbar{{\sl (iv) Optimal Recombination and Solution
Space Navigation}}
For fairly general 3D constraint systems, there are algorithms with formal
guarantees that
solve the parent (sub)systems that occur in the DR-plan \cite{XX, XX,XX},
provided the DR-plan meets some of the above criteria.
These algorithms  uncover underlying matroids to combinatorially optimize
the algebraic complexity of (re)combining child system solutions,
and algebraically solve the optimized recombination system to give a
solution to the parent system at any
given level of the DR-plan.

However, the generality of these algorithms
trades-off against efficiency, and despite the optimization,
the best algorithms can still take
exponential time in the number of child subsystems in order to guarantee
all solutions even for a single (sub)system in a DR-plan. They
are prohibitively slow in practice. For the entire DR-plan, finding all
solutions is barely tractable even with fast recombination algorithms for
the subsystems in the DR-plan. This is because even for the simplest
systems, the problem is NP-hard \cite{XX} and there is a
combinatorial explosion of solutions \cite{XX}.  Using the DR-plan and
optimal recombination as a principled basis, high performance software
exists \cite{XX,XX} to
tame combinatorial explosion via user intervention.

\medskip\noindent\underbar{{\sl (v) Configuration Spaces of
Underconstrained Systems}}
For underconstrained 2D bar-joint and multibody-pin cusecs obtained from
various subclasses of tree-decomposable systems, algorithms have been
developed \cite{XX, XX} that
to complete them into isostatic systems \cite{XX, XX} and to find paths
within the connected components \cite{XX,XX} of
standard cartesian configuration spaces. Most of the algorithms with
formal guarantees leverage Cayley configuration space theory \cite{XX,XX}
to characterize subclasses of graphs and additional constraints that
control combinatorial explosion, and provide faithful bijective
representation
of connected components and paths.
These algorithms have decreasing efficiency as the subclass of systems
gets bigger,  with highest efficiency for
underlying partial 2-tree graphs (alternately, tree-width 2,
series-parallel, $K_4$ minor avoiding),   moderate efficiency for
1 degree-of-freedom (dof) graphs with low Cayley complexity (which include
common linkages such as the Strandbeest, Limacon and Cardioid), and
decreased efficiency for general 1-dof tree-decomposable graphs. While
software suites exist \cite{XX,XX}, no such formal algorithms and
guarantees are known for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}
The contributions of this paper are the following.
\begin{itemize}
\item
We  navigate the NP-hardness barrier mentioned in (2) above, for finding
optimal DR-plans by defining a
so-called {\it canonical} DR-plan and showing a strong Church-Rosser
property: {\it all canonical DR-plans for isostatic or
underconstrained
2D qusecs are optimal} (Section \ref{dr}).
\item
We give an efficient ($O(n^2)$) algorithm to find a canonical (and hence
optimal) DR-plan for all 3 types of 2D qusecs mentioned above (Sections
\ref{dr} and \ref{app}.
The canonical DR-plan
illuminates the essence of the NP-hardness of finding optimal DR-plans for
overconstrained systems.
\item
We show reductions between different well-known problems related to
realization or solution by
recombining the realizations or solutions of subsystems (at any given level
of the DR-plan). Example problems include optimal completion of
underconstrained  systems  \cite{XX}, and optimal parametrization in
isostatic systems \cite{XX}). When completions and parametrizations are
given from certain well-known classes, we obtain new,
efficient algorithms for realizing both isostatic and underconstrained
qusecs by leveraging recent results about Cayley parameters in
\cite{XX,XX}  (Section \ref{recomb}).
\item
We briefly describe applications of the above techniques to modeling,
analyzing and designing specific properties in 2D material layers.
For Examples 1,2 (achieving isostaticity, distribution of stresses in
self-similar, bar-joint systems); Example 3 (canonical and optimal
DR-plans for pinned line incidence systems \cite{XX}) and Examples 4,5
(boundary-conditions for achieving various desired properties
of multi-body  pin systems).

>>>>

\section{Introduction}
\label{sec:intro}

Some properties of natural and engineered materials can be analyzed  by
treating them as stacked two dimensional (2D) layers.
The structure within each layer could be
self-similar \cite{Intro1}
spanning multiple scales,
generally aperiodic and quasi-uniform within any one scale,
and consisting of a few repeated motifs appearing in disordered
arrangements. Each layer is not necessarily planar, i.e.,
it consists of multiple,
inter-constraining planar (genus 0) monolayers.
Furthermore, a layer is often  either
{\sl isostatic or underconstrained, not
self-stressed} (See Section \ref{sec:prelim} for definitions).
These properties are
consistent with a self-assembled 2D structure that minimizes mass,
optimally distributes external stresses and itself
participates in the assembly of diverse and multifunctional,
larger 2D structures.

@@

\begin{enumerate}
  %
    \item (cross-section) of microtubules \cite{Necklace1} e.g., in
ciliary membranes and transitions \cite{Necklace2}
   %
    \item (cross-section) of hierarchical bone structure \cite{XX} %
    \item crosslinked cellulose or collagen microfibril monolayers e.g.,
in cell-walls \cite{CellWalls1} \cite{CellWalls1}, as well as crosslinked
actin filaments in the cytoskeleton matrix.
  %
    \item more recent, engineered examples including  disordered graphene
layers \cite{Graphene1} \cite{Graphene2} sometimes reinforced
    by  microfibrils; and DNA assemblies \cite{Microfibrils1} including a
recent Sierpinski carpet, bringing other self-similar structures
    \cite{Microfibrils2} within reach.
    %
    \item  silica bi-layers, glass \cite{SilicaGlass1}
\cite{SilicaGlass2}, and materials that behave like assemblies of
    2D particles under non-overlap constraints, e.g, jammed
    disks on the plane \cite{JammedDisk1}
%
\end{enumerate}
%
In order to study structural and mechanical properties
such as rigidity, flexes and distribution of external stresses
within the material layer, it is natural to model a material
layer as a solution of a geometric constraint system
of appropriate types of geometric primitives, under
metric or algebraic constraints.
Such  2D {\bf{\em qusecs}} (quasi-uniform or self-similar
constraint systems) can be used to
understand or design material layers (their solutions)
with desired properties.
%
\subsection{Previous Work on Relevant 2D Geometric Constraint Systems} We
now briefly survey existing techniques for studying 2D {\em qusecs,}  many
of which are {\it bar-joint} systems (Examples 1,2 above, see Sections
\ref{sec:DRP}, \ref{sec:recomb}),
{\it multibody-pin} systems (Example 4,5, see Section \ref{sec:bodypin}) or  {\it
pinned-line incidence} systems (Example 3, see Section \ref{sec:pinnedline}). The
limitations of these techniques directly motivate
the contributions of this paper.

@@

\medskip\noindent\underbar{{\sl (iv) Optimal Recombination and Solution
Space Navigation}}
For the entire DR-plan, finding all
desired solutions is barely tractable even if recombination
of solved subsystems is easy for each indecomposable parent system in the
DR-plan.
This is because even for the simplest, highly decomposable systems
with small DR-plans, the problem of finding even a single
solution to the input system at the root of the DR-plan
is NP-hard \cite{XX} and there is a
combinatorial explosion of solutions \cite{XX}. Typically, however,
the desired solution has a given orientation type, in which case,
the crux of the difficulty is concentrated in the algebraic complexity of
(re)combining child system solutions, to give a
solution to the parent system at any
given level of the DR-plan.
For fairly general 3D constraint systems,
there are algorithms with formal
guarantees that uncover underlying matroids to combinatorially
obtain an optimal parameterization to minimize the algebraic
complexity of the indecomposable parent (sub)systems that occur in the
DR-plan \cite{XX, XX,XX},
provided the DR-plan meets some of the abovementioned criteria.

However, the generality of these algorithms
trades-off against efficiency, and despite the optimization,
the best algorithms can still take
exponential time in the number of child subsystems (which can be arbitrarily
large even for optimal DR-plans) in order to guarantee
all solutions of a given orientation type,
even for a single (sub)system in a DR-plan. They
are prohibitively slow in practice. We note that utilizing the DR-plan and
optimal recombination as a principled basis, high performance heuristics
and software
exists \cite{XX,XX} to
tame combinatorial explosion via user intervention.

\medskip\noindent\underbar{{\sl (v) Configuration Spaces of
Underconstrained Systems}}
For underconstrained 2D bar-joint and multibody-pin cusecs obtained from
various subclasses of tree-decomposable systems, algorithms have been
developed \cite{XX, XX} that
to complete them into isostatic systems \cite{XX, XX} and to find paths
within the connected components \cite{XX,XX} of
standard cartesian configuration spaces. Most of the algorithms with
formal guarantees leverage Cayley configuration space theory \cite{XX,XX}
to characterize subclasses of graphs and additional constraints that
control combinatorial explosion, and provide faithful bijective
representation
of connected components and paths.
These algorithms have decreasing efficiency as the subclass of systems
gets bigger,  with highest efficiency for
underlying partial 2-tree graphs (alternately, tree-width 2,
series-parallel, $K_4$ minor avoiding),   moderate efficiency for
1 degree-of-freedom (dof) graphs with low Cayley complexity (which include
common linkages such as the Strandbeest, Limacon and Cardioid), and
decreased efficiency for general 1-dof tree-decomposable graphs. While
software suites exist \cite{XX,XX}, no such formal algorithms and
guarantees are known for non-tree-decomposable systems.
%
\subsection{Contributions and Organization}
\label{sec:cont}
The contributions of this paper are the following.
\begin{itemize}
\item
We  navigate the NP-hardness barrier mentioned in (2) above, for finding
optimal DR-plans by defining a
so-called {\it canonical} DR-plan and showing a strong Church-Rosser
property: {\it all canonical DR-plans for isostatic or
underconstrained
2D qusecs are optimal} (Section \ref{sec:DRP}).
\item
We give an efficient ($O(n^2)$) algorithm to find a canonical (and hence
optimal) DR-plan for all 3 types of 2D qusecs mentioned above (Sections
\ref{sec:DRP}, \ref{sec:bodypin}, and \ref{sec:pinnedline}.
The canonical DR-plan
illuminates the essence of the NP-hardness of finding optimal DR-plans for
overconstrained systems.
\item
We give a method to deal with the
algebraic complexity of recombining the realizations or
solutions of  child subsystems into a solution of the parent system.
Specifically, we define the problem of  minimally modifying the
indecomposable recombination system so that it becomes decomposable via a
 small DR-plan and yet preserves the original
solutions in an efficiently searchable manner. We show formal connection
to well known problems such as optimal completion of
underconstrained  systems  \cite{XX}.  When the required modifications
are bounded, we obtain new, efficient algorithms for
realizing both isostatic and underconstrained
qusecs by leveraging recent results about Cayley parameters in
\cite{XX,XX}  (Section \ref{sec:recomb}).
\item
We briefly describe applications of the above techniques to modeling,
analyzing and designing specific properties in 2D material layers.
For Examples 1,2 (achieving isostaticity, distribution of stresses in
self-similar, bar-joint systems); Example 3 (canonical and optimal
DR-plans for pinned line incidence systems \cite{XX}) and Examples 4,5
(boundary-conditions for achieving various desired properties
of multi-body  pin systems).

### 2014-12-15 doc/GMP2015/s02_preliminaries.tex
Major changes to my section. Meera's major changes to her sections. Updated labels and their references.

\section{Preliminaries}\label{prelim}

@@

\begin{definition}
   In the context of this paper, a \textbf{graph} $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$.
\end{definition}

\begin{definition}
    The \textbf{density} of graph $G$ is
    \begin{equation}
        d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}
    \end{equation}
\end{definition}

\begin{definition}
    A graph is \textbf{independent} (or \textbf{sparse}) if, given constant $k$, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.
\end{definition}

@@

\begin{definition}
    A graph is \textbf{over-constrained} if it is not independent.
\end{definition}

@@

\begin{definition}
    A graph is \textbf{well-constrained} (or \textbf{tight}) if, given constant $k$, $G$ is independent and $d(G)=k$.
\end{definition}

\begin{definition}
    A graph is \textbf{rigid} if, given constant $k$, there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.
\end{definition}

\begin{definition}
    A graph is \textbf{under-constrained} if $G$ is independent and not rigid.
\end{definition}

\begin{definition}
    A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an over-constrained graph and (2) all of its subgraphs are also trivial.
    \todo{Maybe leave the following out until it's needed later?}
    In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.
\end{definition}

\begin{definition}
    The \textbf{decomposition-recombination (DR-) plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
    \begin{enumerate}
        \item The root of the tree `contains' $G$.
        \item For all nodes, $C$, that `contain' non-trivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item A node with a trivial subgraph is a leaf.
    \end{enumerate}

@@

    Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.
\end{definition}

\begin{definition}
    The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.
\end{definition}

\begin{definition}
    The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
\end{definition}

@@

$G$ is taken to be a graph with values $(V,E,w_V,w_E)$. The most important limitation of this paper is that we take $G$ to be well-constrained.
\todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

@@

$C$ is an arbitrary graph in a node in $CompleteDRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$. By definition of a DR-plan, it is implied that $C_i$ is a well-constrained vertex-maximal proper subgraph.

>>>>

\section{Preliminaries}
\label{sec:prelim}

@@

In Sections \ref{sec:DRP} and \ref{sec:recomb} a \textbf{graph} is a bar and joint system. $G=(V,E,w_V,w_E)$ is a set of vertices, $V$, and a set of edges, $E$, defined as a tuple of vertices from $V$ (undirected). Additionally, there are two weight functions, $w_V: V \to \mathbb{R}^+$ and $w_E: E \to \mathbb{R}^+$. The \textbf{density} of graph $G$ is $d(G) = \sum_{e\in E}{w_E(e)} - \sum_{v\in V}{w_V(v)}$.

Given a constant $k$, a graph $G$ is:
\begin{itemize}
    \item \textbf{independent} (or \textbf{sparse}) if, for all non-trivial subgraphs $S\subseteq G$, $d(S) \leq k$.

    \item \textbf{over-constrained} if it is not independent.

    \item \textbf{well-constrained} (or \textbf{tight}) if $G$ is independent and $d(G)=k$.

    \item \textbf{rigid} if there exists some spanning subgraph $S\subseteq G$ such that $S$ is well-constrained.

    \item \textbf{under-constrained} if $G$ is independent and not rigid.

    % \item \textbf{trivial} if (1) it is over-constrained graph and (2) all of its subgraphs are also trivial. Trivial graphs are input.
\end{itemize}

\textbf{Trivial} graphs are ill-defined in the general case. The only strict requirements are: (1) it must over-constrained and (2) all of its subgraphs are also trivial.

@@

@@

% \begin{definition}
%     A \textbf{trivial} graph is ill-defined in the general case. The only strict requirements are: (1) it must be an over-constrained graph and (2) all of its subgraphs are also trivial.
%     \todo{Maybe leave the following out until it's needed later?}
%     In the familiar geometric cases of $d$-dimensional space, all vertex weights are $d$, all edge weights are $1$, and constant $k= -{{d+1}\choose{2}}$. Trivial graphs for 2D would be a single vertex. Trivial graphs in 3D would be a vertex and an edge (2 vertices with an edge between). Etc. These trivial graphs capture the notion of the rotational symmetry that exists in geometric spaces.
% \end{definition}

\begin{definition}\label{def:drp}
    The \textbf{decomposition-recombination \mbox{(DR-)} plan} of graph $G$, $DRP(G)$, is defined as a tree that has the following properties:
    \begin{enumerate}
        \item The root of the tree `contains' $G$.
        \item For all nodes, $C$, that `contain' non-trivial graphs, its $N$ children, $C_1, \ldots, C_N$, are trivial or well-constrained vertex-maximal proper subgraphs of that node $C$.
        \item The vertex set of $\bigcup_{i=1}^N{C_i}$ is the vertex set of $C$.
        \item A node with a trivial subgraph is a leaf.
    \end{enumerate}

@@

    Note that nodes will be referred to interchangeably as ``the node that contains the (sub)graph $C$'' and as simply ``$C$''.

    A DR-plan is \textbf{complete} if it satisfies the modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. This makes rule 3 implicit. The complete DR-plan is unique.

    A DR-plan is \textbf{optimal} if it minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
\end{definition}

% \begin{definition}
%     The \textbf{complete DR-plan} of graph $G$, $CompleteDRP(G)$, is the unique DR-plan but with a modified rule number 2: the children are \emph{all} of the trivial or well-constrained vertex-maximal proper subgraphs of that node $C$. By this, rule 3 is implicit for a complete DR-plan.
% \end{definition}

% \begin{definition}
%     The \textbf{optimal DR-plan} of graph $G$, $OptimalDRP(G)$, is the DR-plan that minimizes the maximum fan-in over all nodes in the tree. It is not necessarily unique.
% \end{definition}

@@

In Sections \ref{sec:DRP} and \ref{sec:recomb}, $G$ is taken to be a \emph{well-constrained} bar and joint graph with values $(V,E,w_V,w_E)$.
% \todo{I don't think the following is actually necessary to mention...} To keep problems meaningful we assume that $G$ is connected, as the methods discussed are used to solve systems of equations to establish linkages. It is not useful to solve for two bodies simultaneously if there are no constraints between them.
% THIS MEANS NO EDGES MAY BE LEFT OUT, ALSO.

@@

$C$ is the graph in an arbitrary node in $CompleteDRP(G)$. $C_i$ is the $i^{\text{th}}$ child of $C$. By definition of a DR-plan, it is implied that $C_i$ is a well-constrained vertex-maximal proper subgraph.

### 2014-12-15 doc/GMP2015/s07_problempinning.tex
Major changes to my section. Meera's major changes to her sections. Updated labels and their references.

\section{Problem Pinning}

@@

\begin{remark}
    A multi-body-pin qusec is a special case of bar-joint qusecs that we have been studying. As such, the DR planning discussed in Sections \ref{dr} and \ref{recomb} will still go through.
\end{remark}

@@

In this section we will go over 2 subclasses of multi-body-pin qusecs for modeling Examples 4 and 5 in Section \ref{intro}.

@@

Body-pin qusecs are of particular interest to us in the context of Example 4 in \ref{intro}. Multi-triangle-pin qusec can be used to reprsent the silica bi-layers described in Example 5 of \ref{intro}, where each triangle is the junction of ``disks''. Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR plan:

@@

We can develop the notion of a canonical DR plan for certain $(k,l)$ tightness conditions similar to the way we did in Section \ref{dr}.

@@

\begin{remark}
    All $(k,l)$ tight canonical DR plans are optimal. We can find such a DR plan in the same time complexity as the $(2,3)$ tight case for bar and joint qusecs discussed in Section \ref{dr}.
\end{remark}

\begin{theorem}
    There is a quadratic algorithm for the 1 dof and 2 dof optimal completion problem of Seciton \ref{recomb} for body-pin and multi-triangle-pin qusecs.
\end{theorem}

>>>>

\section{Problem Pinning}
\label{sec:bodypin}

@@

\begin{remark}
    A multi-body-pin qusec is a special case of bar-joint qusecs that we have been studying. As such, the DR planning discussed in Sections \ref{sec:DRP} and \ref{sec:recomb} will still go through.
\end{remark}

@@

In this section we will go over 2 subclasses of multi-body-pin qusecs for modeling Examples 4 and 5 in Section \ref{sec:intro}.

@@

Body-pin qusecs are of particular interest to us in the context of Example 4 in \ref{sec:intro}. Multi-triangle-pin qusec can be used to reprsent the silica bi-layers described in Example 5 of \ref{sec:intro}, where each triangle is the junction of ``disks''. Typically, these systems are not isostatic, so to relate the work of this paper to the systems, we define a slightly different kind of DR plan:

@@

We can develop the notion of a canonical DR plan for certain $(k,l)$ tightness conditions similar to the way we did in Section \ref{sec:DRP}.

@@

\begin{remark}
    All $(k,l)$ tight canonical DR plans are optimal. We can find such a DR plan in the same time complexity as the $(2,3)$ tight case for bar and joint qusecs discussed in Section \ref{sec:DRP}.
\end{remark}

\begin{theorem}
    There is a quadratic algorithm for the 1 dof and 2 dof optimal completion problem of Seciton \ref{sec:recomb} for body-pin and multi-triangle-pin qusecs.
\end{theorem}

### 2014-12-15 doc/GMP2015/s08_pinnedline.tex
Major changes to my section. Meera's major changes to her sections. Updated labels and their references.

\section{Application: finding optimal DR-plans and realizations for cross-linking microfibrils }

@@

\begin{figure}
  \centering
  \includegraphics[width=.9\linewidth]{img/pinned}
\caption{ A well-constrained pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{dr}
to give the Optimal DR-plan for 2-dimensional pinned line incidence graphs.
First, we note the following differences of pinned line incidence graphs from the bar-joint graphs.

@@

With the above modification, 
we now adapt Theorem~\ref{t1} %, the optimal DR-plan for 2-dimensional bar-joint graphs,
for the optimal DR-plan for 2-dimensional pinned line incidence graphs.

@@

The following lemma serves a similar function to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection} 
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection}, 
and can be proved using a similar counting based argument.

@@

Proofs of Lemma~\ref{wc-l2} and \ref{wc-c1} straightforwardly extend to 2-dimensional pinned line incidence graphs 
given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan.
Now we  show that Lemma~\ref{wc-l3} also holds.

\begin{proof}[Proof of Lemma~\ref{wc-l3} for 2D pinned line incidence graphs]
We use the same notations as in the original proof of Lemma~\ref{wc-l3} in Section~\ref{sec:infer_parent}.

@@

Then we analyze all the possible cases for $C_k$.
\begin{itemize}
%    \item 4 cases: $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$ because these are all disconnected (Corollary~\ref{wc-c1}) and by our modified requirement of DR-plan nodes.
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{wc-l2} that $C_k\cup C_i$ cannot be well-constrained. 
    By Lemma~\ref{lem:pinned_union_intersection}, it must be under-constrained, 
    so one of $C_i$ and $C_k$ must be an edge, contradicting the assumption that both $C_i$ and $C_k$ are well-constrained.
%    We also know it cannot be trivial because it contains well-constrained subgraphs. This means it must be under-constrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is well-constrained, thereby contradicting the assumption that $C_k$ is well-constrained.

@@

The following lemma serves as Lemma~\ref{uc-l2} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}

Given Lemma~\ref{wc-l3} and Lemma~\ref{lem:vertex_intersection}, 
it is straightforward to adapt the proof of Theorem~\ref{uc-t1} and \ref{wc-t1} 
to  2-dimensional pinned line incidence graphs,
thus proving Corollary~\ref{cor:pinned}. 
Consequently, we can efficiently find the optimal DR-plan for 2-dimensional pinned line incidence graphs using basically the same algorithm as for 2-dimensional bar-joint graphs.
%we can analyze microfibril cross-linkings by finding the optimal DR-plan for  2-dimensional pinned line incidence graphs in the same way as for 2-dimensional bar-joint graphs.

>>>>

\section{Application: finding optimal DR-plans and realizations for cross-linking microfibrils }
\label{sec:pinnedline}

@@

\begin{figure}
  \centering
  % \includegraphics[width=.9\linewidth]{img/pinned}
\caption{ A well-constrained pinned line incidence graph.}
\label{fig:pinned_line}
\end{figure}

@@

In this section, we will adapt the results in Section~\ref{sec:DRP}
to give the Optimal DR-plan for 2-dimensional pinned line incidence graphs.
First, we note the following differences of pinned line incidence graphs from the bar-joint graphs.

@@

With the above modification,
we now adapt Theorem~\ref{theorem:main} %, the optimal DR-plan for 2-dimensional bar-joint graphs,
for the optimal DR-plan for 2-dimensional pinned line incidence graphs.

@@

The following lemma serves a similar function to Lemma~\ref{lemma:union_intersection} in Section~\ref{sec:union_intersection}
%Using similar counting-based argument, %  to Lemma~\ref{t-l1}--\ref{iuc-l1} in Section~\ref{sec:union_intersection},
and can be proved using a similar counting based argument.

@@

Proofs of Lemma~\ref{lemma:wc_intersection_is_C} and \ref{corollary:no_edges_between_diff} straightforwardly extend to 2-dimensional pinned line incidence graphs
given Lemma~\ref{lem:pinned_union_intersection} and the modified definition of DR-plan.
Now we  show that Lemma~\ref{lemma:wc_intersection_makes_all_wc} also holds.

\begin{proof}[Proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} for 2D pinned line incidence graphs]
We use the same notations as in the original proof of Lemma~\ref{lemma:wc_intersection_makes_all_wc} in Section~\ref{sec:infer_parent}.

@@

Then we analyze all the possible cases for $C_k$.
\begin{itemize}
%    \item 4 cases: $C_k$ cannot be $Idc(C,R_i\cup R_j)$, $Idc(C,R'_i\cup R_j)$, $Idc(C,R_i\cup R'_j)$, or $Idc(C,R'_i\cup R'_j)$ because these are all disconnected (Corollary~\ref{wc-c1}) and by our modified requirement of DR-plan nodes.
    \item 1 case: $C_k=Idc(C,R'_i\cup R'_j\cup D_{i,j})$ is not possible. Since $C_k\cup C_i = Idc(C,R'_i\cup R_j\cup D_{i,j})\neq C$ we have from Lemma \ref{lemma:wc_intersection_is_C} that $C_k\cup C_i$ cannot be well-constrained.
    By Lemma~\ref{lem:pinned_union_intersection}, it must be under-constrained,
    so one of $C_i$ and $C_k$ must be an edge, contradicting the assumption that both $C_i$ and $C_k$ are well-constrained.
%    We also know it cannot be trivial because it contains well-constrained subgraphs. This means it must be under-constrained. From Lemma \ref{uc-l1}, we know that $C_k\cap C_i=Idc(C,R'_j\cup D_{i,j})$ must then be trivial. This is impossible because $D_{i,j}$ is well-constrained, thereby contradicting the assumption that $C_k$ is well-constrained.

@@

The following lemma serves as Lemma~\ref{lemma:uc_intersection_makes_all_uc} for pinned line incidence and can be proved similarly.
\begin{lemma}
\label{lem:vertex_intersection}
If $C_i\cap C_j$ is a single vertex, then $\forall k: C_i\cap C_k$ is a single vertex.
\end{lemma}

Given Lemma~\ref{lemma:wc_intersection_makes_all_wc} and Lemma~\ref{lem:vertex_intersection},
it is straightforward to adapt the proof of Theorem~\ref{theorem:main_trivial} and \ref{theorem:main_wellconstrained}
to  2-dimensional pinned line incidence graphs,
thus proving Corollary~\ref{cor:pinned}.
Consequently, we can efficiently find the optimal DR-plan for 2-dimensional pinned line incidence graphs using basically the same algorithm as for 2-dimensional bar-joint graphs.
%we can analyze microfibril cross-linkings by finding the optimal DR-plan for  2-dimensional pinned line incidence graphs in the same way as for 2-dimensional bar-joint graphs.
